Baseline centering problem

### 2018-12-21 paper/tangotd.tex

The Newton update/middle Bellman equation is
\begin{equation}
Z\gets (1+\eta)Z-\eta Z^2+\eta \gamma ZPZ
\end{equation}
which yields (after applying to $\1_{s_1}$ on the left and $\1_{s_2}/\rho(s_2)$
on the right)
\begin{multline}
Z(s_1,s_2)\gets (1+\eta)Z(s_1,s_2)-\eta \E_{s_3\sim \rho}\,
Z(s_1,s_3)Z(s_3,s_2)\,+\\\eta \gamma \E_{s_3\sim\rho,\, s'_3\sim
P(s'_3|s_3)}\,
Z(s_1,s_3)Z(s'_3,s_2)
\end{multline}
which is perfectly samplable. We can simulate the assignment
$Z(s_1,s_2)\gets...$ via gradient descent on the parameters of
$Z(s_1,s_2)$. \footnote{Should we adjust the size of the gradient descent
to get the right change of $Z(s_1,s_2)$? If we just use SGD, since
gradients may change from point to point, the speed may be different at
various states and we depart from Newton. This is clear when $Z$ is very
small: Newton grows exponentially while a standard gradient descent would
make small steps.} (Or via double sampling, which is not problematic here!?)

>>>>

The Newton update/middle Bellman equation is
\begin{equation}
Z\gets (1+\eta)Z-\eta Z^2+\eta \gamma ZPZ
\end{equation}
which yields (after applying to $\1_{s_1}$ on the left and $\1_{s_2}/\rho(s_2)$
on the right)
\begin{multline}
Z(s_1,s_2)\gets (1+\eta)Z(s_1,s_2)-\eta \E_{s_3\sim \rho}\,
Z(s_1,s_3)Z(s_3,s_2)\,+\\\eta \gamma \E_{s_3\sim\rho,\, s'_3\sim
P(s'_3|s_3)}\,
Z(s_1,s_3)Z(s'_3,s_2)
\end{multline}
which is perfectly samplable. We can simulate the assignment
$Z(s_1,s_2)\gets...$ via gradient descent on the parameters of
$Z(s_1,s_2)$. \footnote{Should we adjust the size of the gradient descent
to get the right change of $Z(s_1,s_2)$? If we just use SGD, since
gradients may change from point to point, the speed may be different at
various states and we depart from Newton. This is clear when $Z$ is very
small: Newton grows exponentially while a standard gradient descent would
make small steps.} (Or via double sampling, which is not problematic
here!? but would converge to trivial solutions like $Z=0$ or
$Z=1/(1-\gamma)$, which are repulsive with Newton.)
